---
title: "Esha_exploration"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Uploading the data:

```{r}
library(tidyverse)
library(RColorBrewer)
library(paletteer)
library(janitor)
library(here)
library(skimr)
library(ggthemes)
library(naniar)
library(readr)
```

```{r}
nectar_perflower <- read_csv(here("potential_datasets", "AgriLand_Nectar_perflower.csv"))
```

```{r}
nectar_perflower <- janitor::clean_names(nectar_perflower)
```

```{r}
nectar_perflower
```

```{r}
nectar_perflower %>% 
  separate(species,
           into = c("genus", "species")) %>% 
  separate(bagging_date,
           into = c("bagging_day", "bagging_month", "bagging_year"),
           sep = "/")
```

## Analyses: which habitats have the least and most amount of nectar per flower

Exploration of the data: 

Habitats with the most nectar (using sugar_in_micrograms_flower_24h):
```{r}
nectar_perflower %>%
  group_by(habitat) %>%
  filter(sugar_in_micrograms_flower_24h != "NA") %>%
  summarize(mean_nectar = mean(sugar_in_micrograms_flower_24h)) %>%
  arrange(desc(mean_nectar))
```

Habitats with the least nectar: 
```{r}
nectar_perflower %>%
  group_by(habitat) %>%
  filter(sugar_in_micrograms_flower_24h != "NA") %>%
  summarize(mean_nectar = mean(sugar_in_micrograms_flower_24h)) %>%
  arrange(mean_nectar)
```

Plotting the habitats with the most nectar: 
```{r}
nectar_perflower %>%
  group_by(habitat) %>%
  filter(sugar_in_micrograms_flower_24h != "NA") %>%
  summarize(mean_nectar = mean(sugar_in_micrograms_flower_24h)) %>%
  arrange(desc(mean_nectar)) %>%
  top_n(5) %>%
  ggplot(aes(x = habitat, y = mean_nectar, fill = habitat)) + 
  geom_col() + 
  coord_flip() +
  theme_linedraw()
```

Habitats with the most nectar (using sugarmax_in_micrograms_flower_24h instead):
```{r}
nectar_perflower %>%
  group_by(habitat) %>%
  filter(sugarmax_in_micrograms_flower_24h != "NA") %>%
  summarize(mean_nectar_from_max = mean(sugarmax_in_micrograms_flower_24h)) %>%
  arrange(desc(mean_nectar_from_max))
```

```{r}
nectar_perflower %>%
  group_by(habitat) %>%
  filter(sugarmax_in_micrograms_flower_24h != "NA") %>%
  summarize(mean_nectar_from_max = mean(sugarmax_in_micrograms_flower_24h)) %>%
  arrange(mean_nectar_from_max)
```

Plotting the habitats with the most nectar (using sugarmax instead): 
```{r}
nectar_perflower %>%
  group_by(habitat) %>%
  filter(sugarmax_in_micrograms_flower_24h != "NA") %>%
  summarize(mean_nectar_from_max = mean(sugarmax_in_micrograms_flower_24h)) %>%
  arrange(desc(mean_nectar_from_max)) %>%
  top_n(5) %>%
  ggplot(aes(x = habitat, y = mean_nectar_from_max, fill = habitat)) + 
  geom_col() + 
  coord_flip() +
  theme_linedraw()
```

I'm still playing with this plot. My goal is to make one that includes the temporal aspect of this data:
```{r}
nectar_perflower %>%
  group_by(habitat, year) %>%
  filter(sugarmax_in_micrograms_flower_24h != "NA") %>%
  ggplot(aes(x = year, y = sugar_in_micrograms_flower_24h, color = habitat)) + 
  geom_point() +
  theme_linedraw()
```

I'm gonna keep playing with this: 
```{r}
nectar_perflower %>%
  group_by(habitat, year) %>%
  filter(sugar_in_micrograms_flower_24h != "NA") %>%
  filter(habitat == "street" | habitat == "pond" | habitat == "managed grassland-garden" | habitat == "hedgerow" | habitat == "healthland-mooseland") %>%
  summarize(mean_nectar = mean(sugar_in_micrograms_flower_24h)) %>%
  ggplot(aes(x = habitat, y = mean_nectar, fill = habitat)) + 
  geom_col() + 
  coord_flip() +
  facet_wrap(~year) +
  theme_linedraw()
```
Yikes! This is very problematic! We have no way of seeing how nectar collected varies over the years. 

```{r}
nectar_perflower %>%
  group_by(habitat) %>%
  filter(sugar_in_micrograms_flower_24h != "NA") %>%
  filter(year == "2011")
```

```{r}
nectar_perflower %>%
  group_by(habitat) %>%
  filter(sugar_in_micrograms_flower_24h != "NA") %>%
  filter(year == "2012")
```

```{r}
nectar_perflower %>%
  group_by(habitat) %>%
  filter(habitat == "wetland") %>%
  filter(sugar_in_micrograms_flower_24h != "NA") %>%
  summarize(mean_nectar = mean(sugar_in_micrograms_flower_24h)) %>%
  ggplot(aes(x = habitat, y = sugar_in_micrograms_flower_24h, color = habitat)) + 
  geom_col() +
  theme_linedraw() 
```


