---
title: "Lean_data_exploration_2/15"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(RColorBrewer)
library(paletteer)
library(janitor)
library(here)
library(skimr)
library(ggthemes)
library(naniar)
library(readr)
```

This is a preloading of the data. The original publication can be found [here](https://doi.org/10.1038/nature16532) and it was also mentioned in [this paper.](https://doi.org/10.1111/2041-210X.12779).
```{r}
nectar_perflower <- read_csv(here("potential_datasets", "AgriLand_Nectar_perflower.csv"))
```

```{r}
nectar_perflower <- janitor::clean_names(nectar_perflower)
```

```{r}
nectar_perflower
```

```{r}
nectar_perflower %>% 
  separate(species,
           into = c("genus", "species")) %>% 
  separate(bagging_date,
           into = c("bagging_day", "bagging_month", "bagging_year"),
           sep = "/")
```

"There is considerable concern over declines in insect pollinator communities and potential impacts on the pollination of crops and wildflowers."



### Possible Analyses
1. genus and species present in each habitat
2. which habitats have the least and most amount of nectar per flower
3. how temperature and humidity affect the amount of nectar per flower
4. how flower #, age, and sex affect the amount of nectar per flower

-Which combinations of factors result in the least and most amount of nectar per flower? 
  (amount of nectar is correlated to amount of pollinators bc flowers use nectar to attract pollinators)


-Why are insect pollinator communities declining?
